---
title: "linear_models"
author: "Longyi Zhao"
date: "2023-11-09"
output: github_document
---
```{r}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6, 
  out.width = "90%"
)

theme_set (theme_minimal() +theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis", 
  ggplots.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_disrete = scale_fill_viridis_d

set.seed(1)
```

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |>
  mutate(stars = review_scores_location/2) |>
  select(
    price, stars, borough = neighbourhood_group, 
    neighbourhood, room_type) |>
  filter(borough != "Staten Island")
```

Let's fit a model!!
```{r}
fit = lm(price ~ stars +borough, data = nyc_airbnb)
```

```{r}
fit = nyc_airbnb |>
  lm(price~stars + borough, data = _)
```

take a look at the fit by using summary(fit) in the console
Not very useful methods
```{r}
# summary(fit)
# summary(fit)$coef
# coef(fit)
# fitted.values(fit)
```

tidy up the output instead
```{r}
fit |>
  broom::glance()
```

tidy up the coefficient, this is more useful 
```{r}
fit |>
  broom::tidy() |>
  mutate(term = str_replace(term, "^borough", "Borough: ")) |>
  select(term, estimate, p.value) |>
  knitr::kable(digits = 3)
```

```{r}
fit = nyc_airbnb |>
  mutate(borough = fct_infreq(borough), 
         room_type = fct_infreq(room_type))|>
  lm(price ~ stars +borough + room_type, data = _) 

fit |>
  broom :: tidy()
```

## Quick look at regression diagnostics

The modelr package can be used to add residuals and fitted values to a dataframe
can use modelr to manipulate 
for example plot the residual 
```{r}
nyc_airbnb |>
  modelr::add_residuals(fit) |>
  ggplot(aes(x = borough, y = resid)) +
  geom_violin() 

nyc_airbnb |>
  modelr::add_residuals(fit) |>
  ggplot(aes(x = stars, y = resid)) +
  geom_point() 

```

## Hypothesis testing for caregorical predictor

fit a "null" and "alternative" model 

```{r}
fit_null = lm (price ~ stars + borough, data = nyc_airbnb)
fit_alternative = lm (price ~ stars + borough + room_type, data = nyc_airbnb)

anova(fit_null, fit_alternative) |>
  broom::tidy()
```

## Borough-level differences
* itneractions
star ratings and room type affects price differently in each borough. 
```{r}
fit = 
  nyc_airbnb |>
  lm(price ~ stars * borough + room_type * borough, data = _)

fit |>
  broom::tidy()
```

nesting columns? 
nest within boroughs and fit borough-specific models associating price with rating and room type

separate model to fit different borough
nest dataset
fit each dataset
```{r}
airbnb_lm = function(df) {
  lm(price ~ stars + room_type, data = df)
}


nyc_airbnb |>
  nest(df = -borough) |>
  mutate(
    models = map(df, airbnb_lm), 
    results = map(models, broom::tidy)
  ) |>
  select(borough, results) |>
  unnest(results) |>
  select(borough, term, estimate) |>
  pivot_wider(
    names_from = term, 
    values_from = estimate
  ) |>
  knitr::kable(digits = 2)
```

same thing but just a little difference

```{r}
nyc_airbnb |>
  nest(df = -borough) |>
  mutate(
    models = map(df, \(df) lm(price~stars + room_type, data = df)), 
    results = map(models, broom::tidy)
  ) |>
  select(borough, results) |>
  unnest(results) |>
  select(borough, term, estimate) |>
  pivot_wider(
    names_from = term, 
    values_from = estimate
  ) |>
  knitr::kable(digits = 2)
```

## Binary outcomes, homicide in baltimore 
```{r}
baltimore_df = 
  read_csv("data/homicide-data.csv") |> 
  filter(city == "Baltimore") |> 
  mutate(
    resolved = as.numeric(disposition == "Closed by arrest"),
    victim_age = as.numeric(victim_age),
    victim_race = fct_relevel(victim_race, "White")) |> 
  select(resolved, victim_age, victim_race, victim_sex)
```

fitting a logistirc regression 

```{r}
fit_logistic = 
  baltimore_df |> 
  glm(resolved ~ victim_age + victim_race + victim_sex, 
      data = _, 
      family = binomial()) 
```

look at model results
```{r}
fit_logistic |> 
  broom::tidy() |> 
  mutate(OR = exp(estimate)) |>
  select(term, log_OR = estimate, OR, p.value) |> 
  knitr::kable(digits = 3)
```



















